Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-07-08 MUSES_vs_BYOD_solutions.tex

The tool manages all employees' smartphones and tablets from a single-based console. This console monitors the devices since the initial set up and registration, until they log off. Remainder features are similar to IBM's product, adding some new such as the incorporation of a service called Malware and Web protection, so that there is no need for having a previously installed antivirus in the devices.

With regard to compliance enforcement, the main goal of this Mobile Control tool is to give more importance to company security, instead of giving more flexibility to the users. But it has been demonstrated by Herath and Rao in \cite{SecPolPenalty09} that this practise can result in bad users' behaviour, even not on purpose. Thus, the company BYOD initiative should include an acceptable use policy to ensure that the users are aware of the measures that the company would take if a device breaches any ISPs. Sophos aims to reach this by doing three main tasks: First, by allowing setting up user and group-based security policies separately. Secondly, by a risk mitigation in which the actions to perform can be set according to the severity of the breach. For minor cases, the company may want to simply inform to the user, but if sensitive data is at risk, a remote wipe may be the chosen option. Finally, compliance check, by constantly performing scans to detect malware and putting the devices in quarantine when they are found infected.

>>>>

The tool manages all employees' smartphones and tablets from a single-based console. This console monitors the devices since the initial set up and registration, until they log off. Remainder features are similar to IBM's product, adding some new such as the incorporation of a service called Malware and Web protection, so that there is no need for having a previously installed antivirus in the devices. Also, version 4.0 adds a new version of what has been called `Sophos Antivirus Engine', with offline detection capabilities.

With regard to compliance enforcement, the main goal of this Mobile Control tool is to give more importance to company security, instead of giving more flexibility to the users. But it has been demonstrated by Herath and Rao in \cite{SecPolPenalty09} that this practise can result in bad users' behaviour, even if it was not on purpose. Thus, the company BYOD initiative should include an acceptable use policy to ensure that the users are aware of the measures that the company would take if a device breaches any ISPs. Sophos aims to reach this by doing three main tasks: First, by allowing setting up user and group-based security policies separately. Secondly, by a risk mitigation in which the actions to perform can be set according to the severity of the breach. For minor cases, the company might want to simply inform to the user, but if sensitive data is at risk, a remote wipe might be the chosen option. Finally, compliance check, by constantly performing scans to detect malware and putting the devices in quarantine when they are found infected.

### 2015-07-08 table_taxonomy.tex

\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

@@

  \centering
%  \renewcommand{\arraystretch}{1.2}% Spread rows out...
  \resizebox{14cm}{!}{
  \begin{tabular}{>{\centering\bfseries}m{1in} >{\centering}m{1in} >{\centering}m{1in} >{\centering}m{1in} >{\centering}m{1in} >{\centering\arraybackslash}m{1in}}
    \toprule
      & \textbf{Online threat detection method} & \textbf{Updatable database information} & \textbf{Standalone} & \textbf{Non-invasive data access} & \textbf{Superuser system control} \\
    \midrule
    MUSES & \cmark & \xmark & & &  \\
     \arrayrulecolor[gray]{0.8}\hline
    IBM Mobile Security & & & & &  \\
     \arrayrulecolor[gray]{0.8}\hline
    Sophos Mobile Control & & & & &\\
     \arrayrulecolor[gray]{0.8}\hline
    Samsung Knox and Blackbery Balance & & & & &\\
     \arrayrulecolor[gray]{0.8}\hline
    Blackphone & & & & &\\
     \arrayrulecolor[gray]{0.8}\hline
    Android for Work & & & & &\\
    \bottomrule
  \end{tabular}
  }
  \caption{Features of the analyzed products considering licenses, type of devices and price.}
\end{table}

>>>>

\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\nmark}{\scalebox{1.25}{\textbf{-}} }

@@

  \centering
  \renewcommand{\arraystretch}{1.8}% Spread rows out...
%  \resizebox{14cm}{!}{
  \begin{tabular}{>{\centering\bfseries}m{0.8in} >{\centering}m{0.8in} >{\centering}m{0.8in} >{\centering}m{0.8in} >{\centering}m{0.8in} >{\centering\arraybackslash}m{0.8in}}
    \toprule
      & \textbf{Offline threat detection method} & \textbf{Updatable database} & \textbf{Standalone} & \textbf{Non-invasive data access} & \textbf{Superuser system control} \\
    \midrule
    MUSES & \cmark & \cmark & \cmark & \cmark & \cmark  \\
     \arrayrulecolor[gray]{0.8}\hline
    IBM Mobile Security & \xmark & \xmark & \cmark & \xmark & \xmark  \\
     \arrayrulecolor[gray]{0.8}\hline
    Sophos Mobile Control & \xmark & \xmark & \cmark & \nmark & \nmark \\
     \arrayrulecolor[gray]{0.8}\hline
    Samsung Knox and Blackbery Balance & \nmark & \nmark & \cmark & \nmark & \nmark\\
     \arrayrulecolor[gray]{0.8}\hline
    Blackphone & \nmark & \nmark & \cmark & \nmark & \nmark\\
     \arrayrulecolor[gray]{0.8}\hline
    Android for Work & \nmark & \nmark & \cmark & \nmark & \nmark\\
    \bottomrule
  \end{tabular}
%  }
  \caption{Proposed taxonomy to classify the BYOD tools described in this paper.}
\end{table}
